Missing Data

### 2021-06-11 analysis/missing.Rmd
fix: wrong plot call

    plot.window(xlim = xlim, ylim = c(0L, n + 1L))
    title(main = "Missing Data", adj = 0L)
    title(xlab = "Frequency", adj = 1L)
    y <- seq_len(n)
    mtext(
        names(x), at = y, adj = 0L, side = 2L, las = 2L,
        line = (w + 0.1) / par("csi"), cex = 0.8
    )
    abline(h = y, col = "#808080", lty = "dotted", lwd = 1L)
    points(x, y, col = col, pch = pch)
    axis(1L, lwd.ticks = 0L, col = "#808080")
}

@@

    y <- seq_len(nc)
    image(
        1L:nr, y, x[, rev(y)], col = col,
        xlim = 0.5 + c(0L, nr), ylim = 0.5 + c(0L, nc),
        axes = FALSE, xlab = "", ylab = ""
    )
    title(main = "Missing Data", adj = 0L)
    title(xlab = "Rows", adj = 1L)
    mtext(
        rev(nms), at = y, adj = 0L, side = 2L, las = 2L,
        line = (w + 0.1) / par("csi"), cex = 0.8
    )
    abline(h = y, col = "#808080", lty = "dotted", lwd = 1L)
}
```

>>>>

    plot(NA, xlim = xlim, ylim = c(0L, n + 1L), axes = FALSE)
    title(main = "Missing Data", adj = 0L)
    title(xlab = "Frequency", adj = 1L)
    y <- seq_len(n)
    mtext(
        names(x), at = y, adj = 0L, side = 2L, las = 2L,
        line = (w + 0.1) / par("csi"), cex = 0.8
    )
    abline(h = y, col = "#808080", lty = "dotted", lwd = 1L)
    points(x, y, col = col, pch = pch)
    axis(1L, lwd.ticks = 0L, col = "#808080")
}

@@

    y <- seq_len(nc)
    image(
        1L:nr, y, x[, rev(y)], col = col,
        xlim = 0.5 + c(0L, nr), ylim = 0.5 + c(0L, nc),
        axes = FALSE, xlab = "", ylab = ""
    )
    title(main = "Missing Data", adj = 0L)
    title(xlab = "Rows", adj = 1L)
    mtext(
        rev(nms), at = y, adj = 0L, side = 2L, las = 2L,
        line = (w + 0.1) / par("csi"), cex = 0.75
    )
    abline(h = y, col = "#808080", lty = "dotted", lwd = 1L)
}
```
